### 2017-05-11 Publications/Original Software Publications/Science of Computer Programming/reply letter/letter.tex
updating reply letter
Signed-off-by: Felipe R. Monteiro <rms.felipe@gmail.com>

\begin{quote}
\textcolor{blue}{\textbf{Response:} Response.}
\end{quote}

@@

>>>>

\begin{quote}
\textcolor{blue}{\textbf{Response:} We really appreciate the reviewer's summary about our work, which fairly describes the main contributions of our manuscript. We also appreciate the reviewer's comments and also his/her effort to provide relevant comments to improve our paper. We have carefully revised our manuscript, considering all valuable and constructive comments/suggestions.}
\end{quote}

@@

    \begin{quote}
    \textcolor{blue}{\textbf{Response:} We have fixed this typo.}
    \end{quote}
